Individual Partisan Harm and Utility in Redistricting

### 2021-10-20 paper/paper.Rmd
1-1 and many-many appendix
@CoryMcCartan does this fit in the main paper or should it be appendix material?

If main paper, we probably want a figure that shows the idea?

>>>>

# Misrepresentation Map

The intuition that drives these measures is the misrepresentation map.
Consider a state that is partitioned into smaller geographies, typically called precincts or voter tabulation districts.
These units act as the atoms of redistricting.
We assume that they are not split in the redistricting process.
Thus, districts are made of whole precincts.
For a given precinct, we can thus calculate the expected party share of the district that a precinct is in for any given plan.
The expected party share can take many forms, as mentioned in *Modeling Election Outcomes*.
By combining the information about the geographic precinct, we can measure the expected party share that an individual living in that precinct would expect to experience.

Visually, we can consider a map colored by party share of the district that each precinct is assigned to.
Most often, we represent this in a blue to red gradient which offers the typical Democratic or Republican representative dynamic.
Given a counterfactual, we can then take the difference of the expected party share, precinct-by-precinct.
This offers a precinct-level coloration based on difference in expected party share at the district level.
In the typical two-party scenario, using Democratic two-party vote share, a positive difference would indicate that the individuals in those precincts are likely to be represented by Democrats.
A negative difference would indicate that the individuals in those precincts are likely to be represented by Republicans.
Thus, positives would be map-matically represented by blues and negatives by reds.

Note that this takes a similar visual form as a dislocation map, though these are conceptually distinct [@defoeubarodd21].
The dislocation map indicates within a single plan how nearby individuals are likely or unlikely to be represented by the same party.

We focus largely on the case of a misrepresentation map that is the difference between a single enacted districting plan and an ensemble of alternate, legal districting plans.
This does not need to be the case, however.
A misrepresentation map can indicate the difference between two singular maps, calculating the difference in expected district-level party representation.
This would allow direct computation of utility, fairness, or other metrics based on the difference in the two maps.
Similarly, given two sets of ensembles, likely generated under different target distributions, we can create a similar misrepresentation map that would allow us to estimate interesting measures, such as the differential harm caused by the inclusion of an additional criteria in state district drawing rules.
